### 2021-11-09 paper/output/document/paper31.tex
bit more cleaning but really moving on to applications

%
\begin{isabellebody}%
\setisabellecontext{paper{\isadigit{3}}{\isadigit{1}}}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Prior Formalizations of The Categorical Imperative%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this section, I present two formalizations of the categorical imperative and a testing framework
to evaluate them. In Section \ref{sec:naive}, I will consider an intuitive but naive formalization of 
the formula of universal law. This formalization is equivalent to a theorem in my base logic (DDL), so 
thus does not actually increase the power of my base logic. In effect, this formalization serves as a control
group that I use to present the testing architecture used to evaluate following formalizations.
In Section \ref{sec:kroy}, I will explore Moshe Kroy's partial formalization of 
the categorical imperative.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Naive Formalization of the Formula of Universal Law \label{sec:naive}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
This section presents a simple and intuitive formalization of the Formula of Universal Law (FUL). 
This naive formalization will hold in the base logic itself, so this formalization does not actually
improve upon a plain deontic logic at all. This section serves two purposes. First, the naive formalization
is a toy example that demonstrates the implementation and testing process that will be used for the more 
complex formalizations presented later in Chapters 2 and 3. Second, this formalization is effectively
a control group used to determine which properties of obligaition hold in the base logic. Future formalizations
will improve on the base logic by passing more tests, or equivalently, proving more properties of 
obligation than the base logic can.

@@

Let's now consider a naive reading of the Formula of Universal Law (FUL): ``act only in accordance 
with that maxim through which you can at the same time will that it become a universal law" \citep{groundwork}.
An immediate translation to DDL is that if $A$ is not necessary permissible then it is prohibited. In other
words, if we cannot universalize $P A$ (where universalizing is represented by the modal necessity 
operator), then $A$ is prohibited. This sentence is formalized in the abbreviation below:%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ FUL{\isacharunderscore}naive\ \isakeyword{where}\ {\isachardoublequoteopen}FUL{\isacharunderscore}naive\ {\isasymequiv}\ {\isasymlambda}A{\isachardot}\ {\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}{\isasymbox}\ {\isacharparenleft}P\ A{\isacharparenright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}O\ {\isacharbraceleft}{\isacharparenleft}\isactrlbold {\isasymnot}A{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{For a given maxim `A', the FUL states that if A is not necessarily permissible, it is prohibited.%
}%
\begin{isamarkuptext}%
This naive formalization holds as a theorem of DDL. I show this using Isabelle below:%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isasymforall}A{\isachardot}\ {\isasymTurnstile}\ {\isacharparenleft}FUL{\isacharunderscore}naive\ A{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isadelimproof
\ \ %
\endisadelimproof
%
\isatagproof
\isacommand{by}\isamarkupfalse%
\ simp\isanewline
%
\isamarkupcmt{In this short and simple proof, the statement ``by simp" demonstrates that the proof is completed
using the ``simp" tool, which is Isabelle's term rewriting engine. In this case, the result follows from
the definitions of the modal operators in DDL, so term rewriting suffices to complete the proof.%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
The general process of an implementation of a formalization of the FUL will be to represent the 
formalization as a sentence in my logic, as above, and then to add the formalization as an axiom to 
the logic. Kant's ethical theory is rule based, so it involves applying the categorical
imperative to solve ethical dilemmas. In logic, this is equivalent to adopting the categorical imperative as 
an axiom and then reasoning in the newly formed logic to come to ethical conclusions. Adding the categorical
imperative as an axiom makes it impossible to violate it and thus represents the categorical imperative
as the supreme, unviolable law of morality.

@@

Because my naive formalization holds in the base logic, adding it as an axiom does not make the logic
any more powerful. No new theorems can be derived using the naive formalization that could not already
be derived in the base logic. Thus, this section serves as a``control group." Tests performed in this
section establish which properties of obligation don't hold in the base logic. The fact that these 
tests will pass for the later, more sophisticated formalizations will serve as evidence for the superiority
of these formalizations over the base logic.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{axiomatization}\isamarkupfalse%
\ \isakeyword{where}\isanewline
FUL{\isacharunderscore}{\isadigit{1}}{\isacharcolon}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}{\isasymbox}\ {\isacharparenleft}P\ A{\isacharparenright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}O\ {\isacharbraceleft}{\isacharparenleft}\isactrlbold {\isasymnot}A{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
\begin{isamarkuptext}%
Once I add a formalization of the FUL as an axiom to my system, I will test the formalization.
Each test will take the form of a lemma which I expect to either hold or be disproven by the categorical
imperative. For example, one test might be the lemma ``murder is wrong." I will evaluate formalizations
based on their ability to prove expected properties of the categorical imperative, as determined by 
philosophical literature. These tests fall into two categories: metaethical tests, which focus on 
abstract properties of the ethical system, and application tests, which simulate the kind of practical reasoning 
that an agent would actually perform by specifying a simple model.

@@

  Empty assignment \color{black}%
}\isanewline
%
\isamarkupcmt{Nitpick tells us that the FUL is consistent\footnote{``oops" at the end of a lemma indicates that the 
proof is left unfinished. It does not indicate that an error occurred. In this case, we aren't interested
in proving True (the proof is trivial and automatic), hence the oops.}%
}\isanewline
\isanewline
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
An initial property that we might be interested in is the possibility of permissibility, or 
whether or not the system can generate models in which certain acts are permissible. In modern ethics, 
permissibility is a well-accepted phenomenon.
An ethical theory that doesn't allow for permissibility would require that every action is either obligatory or 
prohibited. If that is the case, many counterintuitive theorems follow, including that all 
permissible actions are obligatory.\footnote{Proof is in the appendix.} Therefore, I will include 
the possibility of permissibility as one test for my formalizations.%
\end{isamarkuptext}\isamarkuptrue%
\ \ \isacommand{lemma}\isamarkupfalse%
\ permissible{\isacharcolon}\isanewline
\ \ \ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymexists}A{\isachardot}\ {\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
\ \ \ \ \isacommand{nitpick}\isamarkupfalse%
\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue}Nitpick found a model for card i = 1 and card s = 1:

  Skolem constant:
    A =($\lambda x. \_$)($i_1$ := False) \color{black}%
}\isanewline
%
\isamarkupcmt{I want to show that there exists a model where there is some formula A that is permissible, or, 
in English, that permissibility is possible. Nitpick finds a model where the above formula holds, 
so permissibility is indeed possible.%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
Another similar property is that for any arbitrary action A, there is a model that makes 
it permissible. This property is actually not desirable, because if A is "murder" then the CI should require that 
it be prohibited in every world. Therefore, in order for this test to pass, Nitpick should \emph{not}
be able to find a satisfying model for this formula.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ fixed{\isacharunderscore}formula{\isacharunderscore}is{\isacharunderscore}permissible{\isacharcolon}\isanewline
\ \ \isakeyword{fixes}\ A\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue}Nitpick found a model for card i = 1:

@@

  Free variable:
    A = ($\lambda x. \_$)($i_1$ := False) \color{black}%
}\isanewline
%
\isamarkupcmt{Nitpick finds a counterexample disproving the statement that any arbitrary action is obligatory, so
this test passes.%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
$\textbf{Conflicting Obligations}$%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
The next set of tests will focus on conflicting obligations. There is some debate about Kant's
personal stance on conflicting obligations, but neo-Kantian agree that the FUL itself cannot obligate
conflicting actions. For more complete discussion of conflicting obligations in Kantian literature, 
see \ref{sec:priorgoals}. I will first test whether or not, for some arbitrary action, Nitpick can find
a model in which that action is both obligated and prohibited.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ conflicting{\isacharunderscore}obligations{\isacharcolon}\isanewline
\ \ \isakeyword{fixes}\ A\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue} Nitpick found a model for card i = 2:

>>>>

%
\begin{isabellebody}%
\setisabellecontext{paper{\isadigit{3}}{\isadigit{1}}}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Prior Formalizations of The Categorical Imperative%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this section, I present two formalizations of the categorical imperative and a testing framework
to evaluate them. In Section \ref{sec:naive}, I will consider an intuitive but naive formalization of 
the formula of universal law. This formalization is equivalent to a theorem in my base logic (DDL), so 
thus does not actually increase the power of my base logic. In effect, this formalization serves as a control
group that I use to present the testing architecture used to evaluate following formalizations.
In Section \ref{sec:kroy}, I will explore Moshe Kroy's partial formalization of 
the categorical imperative.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Naive Formalization of the Formula of Universal Law \label{sec:naive}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
This section presents a simple and intuitive formalization of the Formula of Universal Law (FUL). 
This naive formalization will hold in the base logic itself, so this formalization does not actually
improve upon an ordinary deontic logic at all. This section serves two purposes. First, the naive formalization
is a toy example that demonstrates the implementation and testing process that will be used for the more 
complex formalizations presented later in Chapters 2 and 3. Second, this formalization is effectively
a control group used to determine which properties of obligaition hold in the base logic. Future formalizations
will improve on the base logic by passing more tests, or equivalently, proving more properties of 
obligation than the base logic can.

@@

Let's now consider a naive reading of the Formula of Universal Law (FUL): ``act only in accordance 
with that maxim through which you can at the same time will that it become a universal law" \citep{groundwork}.
An immediate translation to DDL is that if $A$ is not necessary permissible then it is prohibited. In other
words, if we cannot universalize $P A$ (where universalizing is represented by the modal necessity 
operator), then $A$ is prohibited. This sentence is formalized in the abbreviation below:%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ FUL{\isacharunderscore}naive\ \isakeyword{where}\ {\isachardoublequoteopen}FUL{\isacharunderscore}naive\ {\isasymequiv}\ {\isasymlambda}A{\isachardot}\ {\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}{\isasymbox}\ {\isacharparenleft}P\ A{\isacharparenright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}O\ {\isacharbraceleft}{\isacharparenleft}\isactrlbold {\isasymnot}A{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{For a given maxim `A', the FUL states that if A is not necessarily permissible, it is prohibited.%
}%
\begin{isamarkuptext}%
This naive formalization holds as a theorem of DDL. I show this using Isabelle below:%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isasymforall}A{\isachardot}\ {\isasymTurnstile}\ {\isacharparenleft}FUL{\isacharunderscore}naive\ A{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isadelimproof
\ \ %
\endisadelimproof
%
\isatagproof
\isacommand{by}\isamarkupfalse%
\ simp\isanewline
%
\isamarkupcmt{In this short and simple proof, the statement ``by simp" demonstrates that the proof is completed
using the ``simp" tool, which is Isabelle's term rewriting engine. In this case, the result follows from
the definitions of the modal operators in DDL, so term rewriting suffices to complete the proof.%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
The general process of implementing a formalization of the FUL will be to represent the 
formalization as a sentence in my logic, as above, and then to add the formalization as an axiom to 
the logic. Kant's ethical theory is rule based, so it involves applying the categorical
imperative to solve ethical dilemmas. In logic, this is equivalent to adopting the categorical imperative as 
an axiom and then reasoning in the newly formed logic to come to ethical conclusions. Adding the categorical
imperative as an axiom makes it impossible to violate it and thus represents the categorical imperative
as the supreme, unviolable law of morality.

@@

Because my naive formalization holds in the base logic, adding it as an axiom does not make the logic
any more powerful. No new theorems can be derived using the naive formalization that could not already
be derived in the base logic. Thus, this section serves as a ``control group." Tests performed in this
section establish which properties of obligation don't hold in the base logic. The fact that these 
tests will pass for the later, more sophisticated formalizations will serve as evidence for the superiority
of these formalizations over the base logic.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{axiomatization}\isamarkupfalse%
\ \isakeyword{where}\isanewline
FUL{\isacharunderscore}{\isadigit{1}}{\isacharcolon}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}{\isasymbox}\ {\isacharparenleft}P\ A{\isacharparenright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}O\ {\isacharbraceleft}{\isacharparenleft}\isactrlbold {\isasymnot}A{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%
\begin{isamarkuptext}%
Once I add a formalization of the FUL as an axiom to my system, I will test the formalization.
Each test will take the form of a lemma which I expect to either hold or be disproven by the categorical
imperative. For example, one test might be the lemma ``murder is wrong." I will evaluate formalizations
based on their ability to prove expected properties of the categorical imperative, as determined by 
philosophical literature. These tests fall into two categories: metaethical tests, which focus on 
abstract properties of the ethical system, and application tests, which simulate the kind of practical reasoning 
that an agent would actually perform by specifying a simple model.

@@

  Empty assignment \color{black}%
}\isanewline
%
\isamarkupcmt{Nitpick tells us that the FUL is consistent\footnote{``oops" at the end of a lemma indicates that the 
proof is left unfinished. It does not indicate that an error occurred. In this case, we aren't interested
in proving True (the proof is trivial and automatic), hence the oops.}%
}\isanewline
\isanewline
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
An initial property that we might be interested in is the possibility of permissibility, or 
whether or not the system can generate models in which certain acts are permissible. In modern ethics, 
permissibility is a well-accepted phenomenon.
An ethical theory that doesn't allow for permissibility would require that every action is either obligatory or 
prohibited. If that is the case, many counterintuitive theorems follow, including that all 
permissible actions are obligatory.\footnote{Proof is in the appendix.} Therefore, I will include 
the possibility of permissibility as one test for my formalizations.%
\end{isamarkuptext}\isamarkuptrue%
\ \ \isacommand{lemma}\isamarkupfalse%
\ permissible{\isacharcolon}\isanewline
\ \ \ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymexists}A{\isachardot}\ {\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
\ \ \ \ \isacommand{nitpick}\isamarkupfalse%
\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue}Nitpick found a model for card i = 1:

  Skolem constant:
    A =($\lambda x. \_$)($i_1$ := False) \color{black}%
}\isanewline
%
\isamarkupcmt{I want to show that there exists a model where there is some formula A that is permissible, or, 
in English, that permissibility is possible. Nitpick finds a model where the above formula holds, 
so permissibility is indeed possible.%
}\isanewline
%
\isamarkupcmt{Quick note on how to read Nitpick results. Nitpick is Isabelle's model checker, and it can either 
time out, find a model that satisfies the given theorem, or find a counterexample that disproves
the given theorem. It will then provide the corresponsing model by specifying model components. For readability, 
all terms except for the free variables are hidden. This model has cardinality 1 for the world (i) type.
The term `A' is defined as false at world $i_1$.%
}\isanewline
%
\isamarkupcmt{These details will be elided for most Nitpick examples, but this provides guidance on how to interpret
the output.%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
Another similar property is that for any arbitrary action A, there is a model that makes 
it permissible. This property is actually not desirable, because if A is "murder" then the CI should require that 
it be prohibited in every world. Therefore, in order for this test to pass, Nitpick should \emph{not}
be able to find a satisfying model for this formula.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ fixed{\isacharunderscore}formula{\isacharunderscore}is{\isacharunderscore}permissible{\isacharcolon}\isanewline
\ \ \isakeyword{fixes}\ A\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue}Nitpick found a model for card i = 1:

@@

  Free variable:
    A = ($\lambda x. \_$)($i_1$ := False) \color{black}%
}\isanewline
%
\isamarkupcmt{Nitpick finds a counterexample disproving the statement that any arbitrary action is obligatory, so
this test passes.%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
$\textbf{Conflicting Obligations}$%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
The next set of tests will focus on conflicting obligations. There is some debate about Kant's
personal stance on conflicting obligations, but neo-Kantians agree that the FUL itself cannot obligate
conflicting actions. For more complete discussion of conflicting obligations in Kantian literature, 
see Section \ref{sec:priorgoals}. I will first test whether or not, for some arbitrary action, Nitpick can find
a model in which that action is both obligated and prohibited.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ conflicting{\isacharunderscore}obligations{\isacharcolon}\isanewline
\ \ \isakeyword{fixes}\ A\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue} Nitpick found a model for card i = 2:

  Free variable:
    A = ($\lambda x. \_$)($i_1$ := False, $i_2$ := True) \color{black}%
}\isanewline
%
\isamarkupcmt{Nitpick found a model with conflicting obligations, so this tests fails.%
}\isanewline
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
The above is a rather weak notion of contradictory obligations. Korsgaard additionally argues that Kantian 
ethics also has the stronger property that if two maxims imply a contradiction, they must not be willed \citep{KorsgaardFUL}.
I test this property below. Because this property is stronger than the previous test, and the previous 
test failed, this test will also fail.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ implied{\isacharunderscore}contradiction{\isacharcolon}\isanewline
\ \ \isakeyword{fixes}\ A{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{fixes}\ B{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\ \isanewline
\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymTurnstile}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}A\ \isactrlbold {\isasymand}\ B{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymTurnstile}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}B{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}\isanewline
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
\isacommand{proof}\isamarkupfalse%
\ {\isacharminus}\ \isanewline
\ \ \isacommand{have}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isasymTurnstile}{\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}{\isasymdiamond}{\isacharparenleft}A\ \isactrlbold {\isasymand}\ B{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
\ \ \ \ \isacommand{by}\isamarkupfalse%
\ {\isacharparenleft}simp\ add{\isacharcolon}\ assms{\isacharparenright}\isanewline
\ \ \isacommand{then}\isamarkupfalse%
\ \isacommand{have}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isasymTurnstile}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A\ \isactrlbold {\isasymand}\ B{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\ \isacommand{by}\isamarkupfalse%
\ {\isacharparenleft}smt\ O{\isacharunderscore}diamond{\isacharparenright}\isanewline
%
\isamarkupcmt{Notice that this is $\textbf{almost}$ the property we are interested in. In fact, if $O \{ A \wedge B \}$
is equivalent to $O\{A\} \wedge O\{B\}$, then the proof is complete.%
}\isanewline
\ \ \isacommand{thus}\isamarkupfalse%
\ {\isacharquery}thesis\ \isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue} Nitpick found a counterexample for card i = 2:

  Free variables:
    A = ($\lambda x. \_$)($i_1$ := True, $i_2$ := False)
    B = ($\lambda x. \_$)($i_1$ := False, $i_2$ := True) \color{black}%
}\isanewline
%
\isamarkupcmt{Sadly the property I'm actually interested in doesn't follow.%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
The above proof yields an interesting observation.  $O \{ A \wedge B \} $ is not equivalent to 
$O\{A\} \wedge O\{B\}$. The rough English translation of  $O \{ A \wedge B \} $ is ``you are obligated to 
do both A and B". The rough English translation of $O\{A\} \wedge O\{B\}$ is ``you are obligated to do A 
and you are obligated to do B." We think those English sentences mean the same thing, so they should mean 
the same thing in our logic as well. This ``distributive" property of obligation is another test.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ distributive{\isacharunderscore}property{\isacharunderscore}for{\isacharunderscore}obligation{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}B{\isacharbraceright}{\isacharparenright}\ {\isasymequiv}\ {\isasymTurnstile}\ O\ {\isacharbraceleft}A\ \isactrlbold {\isasymand}\ B{\isacharbraceright}{\isachardoublequoteclose}\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue} Nitpick found a counterexample for card i = 2:
